\documentclass[10pt]{article}
\usepackage[margin=3cm]{geometry}
\usepackage{array, xcolor, lipsum}
\renewcommand{\familydefault}{\sfdefault}
\usepackage{helvet}
\title{\bfseries\Huge James L. Lendrem \\ Web Developer}

\date{}
\begin{document}
\maketitle

\begin{minipage}[t]{0.48\textwidth}
99 Park Avenue\\
Newcastle Upon Tyne\\
NE3 2LD\\
United Kingdom
\end{minipage}
\begin{minipage}[t]{0.48\textwidth}
\begin{flushright}
Jamlendrem@gmail.com\\
07878426329
\end{flushright}
\end{minipage}

\definecolor{lightgray}{gray}{0.8}
\newcolumntype{L}{>{\raggedleft}p{0.14\textwidth}}
\newcolumntype{R}{p{0.8\textwidth}}
\newcommand\VRule{\color{lightgray}\vrule width 0.5pt}

\section*{Self Motivated and Professional Web Developer.}
Highly motivated professional Web Developer with over 4 years experience including experience working as the senior developer. Projects worked on have been delivered in a time critical manner whilst helping clients increase sales and online conversion rates. Running a company for 2 years has given me the ability to engage confidently with clients. Strong ability to optimise pre-existing websites using PHP and SQL to deliver speed increases greater than 50\%. Object Orientated Programming experience in both PHP and Javascript as well as being a competent front-end developer working in HTML5 and CSS3.

\section*{Skills}
{\bf Languages}\\
PHP, Javascript, HTML, CSS, SASS, SQL, NodeJS, Ruby, and Java.

\section*{Professional Experience}
\begin{tabular}{L!{\VRule}R}
2015--today&{\bf Senior PHP Developer at Kino Creative.}\\
&Senior Developer at Kino Creative. Began as the junior developer then progressed to the senior developer position. Worked on a wide variety of projects over the course of my employment for both small clients and larger clients.\\
&\begin{itemize}
\item Developed Websites using PHP and Wordpress.
\item Implemented Frontend Designs using HTML5, CSS3, and Sass.
\item Engaginged with clients to better understand their needs and help troubleshoot issues they encounter.
\item Established the development process at Kino Creative.
\end{itemize}\\
2013--2015&{\bf Co-Proprietor at Smooth Lines.}\\
&Founded and ran the business Smooth Lines in Hartlepool. We created websites for small and medium sized business in Hartlepool giving companies professional websites for prices that they could afford.\\
&\begin{itemize}
\item Developing Websites using PHP and Joomla.
\item Managing the work schedule.
\item Setting tasks for our work experience intern.
\item Attending business events to promote the company.
\end{itemize}\\
\end{tabular}

\section*{Education}
\begin{tabular}{L!{\VRule}R}
2011--today&{\bf Code School}\\
&Completed over 20 courses on Code School. Including courses in Angular, Express, Ruby, Node, and Mongo DB.\\
2010--2012&{\bf Computer Science at Newcastle University}\\
&Partially completed a Computer Science Degree at Newcastle University. Dropped out in my third year due to personal reasons.\\
&\begin{itemize}
\item First Year - First
\item Second Year - First
\item Third Year - Incomplete
\end{itemize}\\
2008--2010&{\bf A-Levels at Brinkburn Sixth Form College}\\
&A Levels in Computer Science, Mathematics, and Physics with an AS in Further Mathematics
\end{tabular}

\section*{Projects}
{\bf Coastal Retreats -- Company Website}\\
After another developer left Kino Creative I took over the management and maintenance of this project. The client had a number of problems with search queries causing taking large amounts of time to return. It would also cause the site to hang during heavy usage. I successfully managed to analyse this and came to the conclusion database queries where causing the issue. After optimising the queries I reduced response times from 13 seconds to under half a second in most cases.\\
{\bf Luxury Leisure -- Online Training Resource}\\
Successfully developed a online e-learning application for Luxury Leisure - the app was a single page application that allowed Luxury Leisure to train new employees in areas such as Food Safety, and under-age Gambling. It brought their training resources up to date and has successfully increased engagement with material that mostly went unread.\\
{\bf Zespoke -- WebGL Customiser}\\
Created a 3D Customiser using WebGL for a client that sold bespoke furniture. The customiser allowed customers to see a visual representation of their chosen furniture. The customer could then change the colours of the table and add on options such as a glass shelf or table legs and this would be displayed on the visual representation. It also allows customers to move the table around to get a 360 degree view of the table. This has successfully increased engagement with the site.\\
\section*{Interests and Hobbies}
I like to unwind by playing Guitar and enjoy spending time with my friends playing roleplaying games like Dungeons and Dragons and board games. On my evenings I enjoy reading books especially fantasy and medieval fiction. I've also taken part in several hackathons including Ludum Dare, and DevXS.
\end{document}
